Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2017-12-18 WSSSPE4_report/WSSSPE4_paper.tex
minor change in mission and vision section

The participants were 
%given time after the presentation to write down their  
invited to comment,
% Seven people volunteered to work on 
and 
%revising 
the mission and vision statements, were revised 
%incorporating these comments and presenting back to the community.
based on this feedback.
% the committee redrafted the mission and vision.
The committee added focus areas to clarify the organization's breadth and to keep the mission and vision simple and long-lasting.
Comments after the close of the meeting were also incorporated into the statements.
A final draft was put on GitHub and advertised
via the WSSSPE mailing list, Facebook group, and Twitter.
After two weeks without suggested changes, the final statements, 
%as shown below, 
%were added
to the WSSSPE web page (\url{http://wssspe.researchcomputing.org.uk/about-wssspe/}).

>>>>

The participants were 
%given time after the presentation to write down their  
invited to comment,
% Seven people volunteered to work on 
and 
%revising 
the mission and vision statements, were revised 
%incorporating these comments and presenting back to the community.
based on this feedback.
% the committee redrafted the mission and vision.
The committee added focus areas to clarify the organization's breadth and to keep the mission and vision simple and long-lasting.
Comments after the close of the meeting were also incorporated into the statements.
A final draft was put on GitHub and advertised
via the WSSSPE mailing list, Facebook group, and Twitter.
After two weeks without suggested changes, the final statements\footnote{\url{http://wssspe.researchcomputing.org.uk/about-wssspe/}}
%as shown below, 
were added
to the WSSSPE website.
